# Experiment 2

## Hypothesised Effects {#hypothesised-effects-anecdotes-2}

Figures \@ref(fig:plot-simulation-2-negative)
and \@ref(fig:plot-simulation-2-positive) show the simulated data for
the negative and positive valence conditions, respectively. These figures are
different from the equivalent figures in the main text. Here, the same
statistics only value was used for both valence conditions, whereas in the main
text the relevant values for each condition were used. Further, the main text
reports the difference score from the relevant statistics only values, whereas
here the raw means are shown.

(ref:plot-simulation-2-negative) Anecdotes Experiment 2 predicted data for the negative valence condition

```{r plot-simulation-2-negative, fig.cap = "(ref:plot-simulation-2-negative)"}
anecdotes2::plot_simulation$negative
```

(ref:plot-simulation-2-positive) Anecdotes Experiment 2 predicted data for the positive valence condition

```{r plot-simulation-2-positive, fig.cap = "(ref:plot-simulation-2-positive)"}
anecdotes2::plot_simulation$positive
```


## Power Analysis {#power-analysis-2}

A power analysis was conducted through simulation of the effects implied by the
hypotheses in Experiment 2. Data were simulated with the same mean values as
Experiment 1 for the effects that were previously significant (i.e., similarity,
statistics, and interaction effects), and no effect for the differences that
were non-significant (as shown in
Figures \@ref(fig:plot-simulation-2-negative)
and \@ref(fig:plot-simulation-2-positive)). The null effect was
analysed using the two one-sided tests (TOST) procedure, or *equivalence*
testing [@lakens2018], and setting the smallest effect size of interest to the
smallest difference that leads to a significant equivalence between the combined
low similarity and statistics only conditions in Experiment 1.
Figure \@ref(fig:power-analysis-2) shows the results of this analysis,
which suggested a total sample size of `r anecdotes2::power$n_total`
(`r anecdotes2::power$n` $\times$ 2).

\newpage

\blandscape

(ref:power-analysis-2) Anecdotes Experiment 2 power curve. Labels indicate lowest sample size above 80% power.

```{r power-analysis-2, fig.width = 13, fig.height = 7, fig.cap = "(ref:power-analysis-2)"}
anecdotes2::power$power_curve
```

\elandscape

\newpage

## Instructions {#instructions-materials-2-appendix}

Figure \@ref(fig:general-instructions-2) shows the general
instructions all participants received, and
Figures \@ref(fig:specific-instructions-anecdote-only-2), \@ref(fig:specific-instructions-combined-2),
and \@ref(fig:specific-instructions-statistics-only-2) show
the condition-specific instructions.

(ref:general-instructions-2) General instructions for Experiment 2.

```{r general-instructions-2, fig.cap = "(ref:general-instructions-2)"}
file.path(
  materials_2,
  "general_instructions.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-anecdote-only-2) Experiment 2 specific instructions for those in the anecdotes only condition.

```{r specific-instructions-anecdote-only-2, fig.cap = "(ref:specific-instructions-anecdote-only-2)"}
file.path(
  materials_2,
  "specific_instructions_anecdote_condition_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-combined-2) Experiment 2 specific instructions for those in the combined condition.

```{r specific-instructions-combined-2, fig.cap = "(ref:specific-instructions-combined-2)"}
file.path(
  materials_2,
  "specific_instructions_anecdote_condition_combined.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:specific-instructions-statistics-only-2) Experiment 2 specific instructions for those in the statistics only condition.

```{r specific-instructions-statistics-only-2, fig.cap = "(ref:specific-instructions-statistics-only-2)"}
file.path(
  materials_2,
  "specific_instructions_anecdote_condition_statistics_only.png"
) %>%
  image_read() %>%
  image_trim()
```

## Follow-up Questions {#follow-up-materials-2}

Figure \@ref(fig:follow-up-2) shows an example of the
follow-up questions.

(ref:follow-up-2) An example of one of the follow-up question displays in Experiment 2.

```{r follow-up-2, fig.cap = "(ref:follow-up-2)"}
file.path(
  materials_2,
  "follow_up_1.png"
) %>%
  image_read() %>%
  image_trim()
```

## Interstitial Display {#interstitial-materials-2}

Figure \@ref(fig:interstitial-2) shows an example of one of
the interstitial displays.

(ref:interstitial-2) An example of an interstitial display in Experiment 2.

```{r interstitial-2, fig.cap = "(ref:interstitial-2)"}
file.path(
  materials_2,
  "interstitial_1.png"
) %>%
  image_read() %>%
  image_trim()
```

## Similarity Manipulation Check {#results-2-appendix}


The similarity manipulation worked as expected, with the negative anecdote only
low similarity condition being allocated significantly more than those in the
high similarity condition,
`r results_2$allocation$anecdotes_only_similarity$valence_negative`. For
positive anecdotes, participants allocated more to the high similarity condition
than those in the low similarity condition,
`r results_2$allocation$anecdotes_only_similarity$valence_positive`. Evidence
for the similarity manipulation working was also seen in the rating data.
Participants rated anecdotes in the high similarity condition as more similar to
the target than those in the low similarity condition,
`r results_2$follow_up$similarity_rating_similarity`.
