## Method

### Participants

`r descriptives_2$apa` Table \@ref(tab:condition-allocation-2)
shows the allocation of participants to the different conditions. Anecdote
similarity and valence were manipulated within subjects. Therefore, each
participant was assigned to one of two between-subjects evidence type conditions
(anecdote only and anecdote & statistics) and saw five displays (statistics
only, and one of each of the four similarity and valence conditions).
Appendix \@ref(power-analysis-2) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-2}
descriptives_2$condition_allocation_table %>%
  apa_table("Experiment 2 group allocation.")
```

### Materials

#### Instructions

Participants were shown similar instructions to those in Experiment 1. The
general instructions page included a test of the basic information expressed in
the instructions. This test also functioned as an attention check. As in
Experiment 1, participants were also shown instructions that were specific to
their condition. These were shown on the same page as the rest of the project
display, above the case study and focal projects. The instructions clarified
that the anecdote had been randomly sampled and that all anecdotes in the pool
were equally similar to the target project.
Appendix \@ref(instructions-materials-2-appendix) shows the
instructions used in Experiment 2.

#### Allocation Task {#allocation-2}

As in Experiment 1, the allocation task included a table describing the two
focal projects and (apart from the statistics only condition) a description and
analysis of an anecdote.
Figures \@ref(fig:allocation-anecdote-valence-negative-similarity-low-2)
and \@ref(fig:allocation-target-valence-negative-similarity-low-2)
show the anecdote and focal projects, respectively, for the negative valence,
low similarity condition.
Figures \@ref(fig:allocation-anecdote-valence-positive-similarity-high-2)
and \@ref(fig:allocation-target-valence-positive-similarity-high-2)
show the anecdote and focal projects, respectively, for the positive valence,
high similarity conditions. In the statistics only condition, participants were
only shown the focal projects display.

The following were counterbalanced: (a) project variation (five latin square
variations), which is the association of each display content with each
within-subject condition; and (b) anecdote variation (two variations), which is
the association of each project display and being either the target or
comparison project. Table column order and project display order were
randomised.

(ref:allocation-anecdote-valence-negative-similarity-low-2) An example of the anecdote display in the negative valence, low similarity condition of Experiment 2.

```{r allocation-anecdote-valence-negative-similarity-low-2, fig.cap = "(ref:allocation-anecdote-valence-negative-similarity-low-2)"}
file.path(
  materials_2,
  "project_allocation_anecdote_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:allocation-target-valence-negative-similarity-low-2) An example of the focal projects in the negative valence, low similarity condition of Experiment 2. Here, Project 1 was the target project and Project 2 was the comparison project.

```{r allocation-target-valence-negative-similarity-low-2, fig.cap = "(ref:allocation-target-valence-negative-similarity-low-2)"}
file.path(
  materials_2,
  "project_allocation_target_valence_negative_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:allocation-anecdote-valence-positive-similarity-high-2) An example of an anecdote display in the positive valence, high similarity condition of Experiment 2.

```{r allocation-anecdote-valence-positive-similarity-high-2, fig.cap = "(ref:allocation-anecdote-valence-positive-similarity-high-2)"}
file.path(
  materials_2,
  "project_allocation_anecdote_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:allocation-target-valence-positive-similarity-high-2) An example of the focal projects in the positive valence, high similarity condition of Experiment 2. Here, Project 2 was the target project and Project 1 was the comparison project.

```{r allocation-target-valence-positive-similarity-high-2, fig.cap = "(ref:allocation-target-valence-positive-similarity-high-2)"}
file.path(
  materials_2,
  "project_allocation_target_valence_positive_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Interstitial Page

Prior to the display, participants were shown an interstitial page, which was
used to (a) introduce the display and (b) check the participant's attention
(given that no input was required, participants could easily skip the page
without reading the text). See
Appendix \@ref(interstitial-materials-2).

#### Follow-up Questions

Participants were shown similar follow-up questions as in Experiment 1, except
that in Experiment 2, rating scales were 1--7 instead of 1--6. See
Appendix \@ref(follow-up-materials-2) for a sample display of the
follow-up questions.

### Procedure

Participants were introduced to the study via the general instructions page.
They were then shown five sets (presented in a random order) containing three
pages each: an interstitial page, a page showing the allocation task, and a page
with follow-up questions (except for the statistics only condition, in which
participants were not shown the follow-up questions page). The interstitial
pages introduced each display and checked participants' attention to the task.
Each allocation task page contained specific instructions relevant to the
condition followed by the anecdote analysis and description, and the description
of the two focal projects. The only exception was the statistics only display,
for which there was no anecdote description or analysis.
