## Method {#method-1}
### Transparency and openness

```{r, r-packages}
papaja::r_refs(file = "r-references.bib")
my_citations <- papaja::cite_r(
  file = "r-references.bib",
  footnote = TRUE
  )
```

We report how we determined our sample size, all data exclusions, all
manipulations, and all measures in the study. All data, analysis code, and
research materials are available at
https://github.com/shirdekel/anecdotal-bias-in-allocation-decisions
[@dekel2022]. This study's design and its analysis were not pre-registered. The
article used R [Version 4.2.0\; @R-base] [^papaja_pkg_citations] to analyse and
plot the data, generate the experimental materials, and compile the document
itself. This study received approval by The University of Sydney Human Research
Ethics Committee (HREC; Project No.: 2019/056).

`r my_citations$pkgs`

### Participants

`r descriptives_1$apa` Three participants were removed from the data because
they reported being younger than 18.
Table \@ref(tab:condition-allocation-1) shows the allocation of
participants to the different conditions.
Appendix \@ref(power-analysis-1) describes the power analysis
conducted to arrive at this sample size.

```{r condition-allocation-1}
descriptives_1$condition_allocation_table %>%
  apa_table("Experiment 1 group allocation.")
```

### Materials {#materials-1}

#### Instructions {#instructions-materials-1}

All participants were first shown general instructions explaining the task.
Subsequent instructions shown to participants depended on their experimental
condition. Those in the anecdote only condition were told that they would be
shown a case study of a failed project and an analysis of why it failed. Those
in the statistics only condition were told that they would be shown NPV and
reliability information for two focal projects. They were told that these values
were sourced from a study with a large sample. Those in the anecdote &
statistics condition were shown both of these instructions and were also told
that the information in the anecdote had been included in the aggregated study
data. Those in the anecdote & enhanced statistics condition were shown the same
instructions as those in the anecdote & statistics condition, but were also
provided with the explanation of scientific thinking used by @wainberg2018.
Appendix \@ref(instructions-materials-1-appendix) shows the
instructions used in Experiment 1.

#### Allocation Task

In the allocation task, participants were asked to allocate a hypothetical
budget to one of two projects from two different businesses. In this study,
these projects are referred to as the *focal* projects, with one being the
*target* project and the other the *comparison* project. The target project was
used as the reference for the similarity manipulation. That is, the anecdote was
either high or low in similarity to the target project. Further, the data
analyses presented in the Results section used allocations to the target project
as the dependent variable. The comparison project was simply the other focal
project to which participants were allocating. It was a different type of
project to both the target and anecdote projects and was the same for all
participants.

Participants were presented with information about the name, location,
integration (vertical or horizontal)[^integration], and organisational structure
(centralised or decentralised)[^structure] of each business. Further, they were
presented with information about the features of each project that are typically
available to managers prior to investment. Participants in the anecdote only
condition were shown only this information (see
Figure \@ref(fig:allocation-anecdote-only-1)). Those
in the anecdote & statistics, anecdote & enhanced statistics, and statistics
only conditions were shown this information along with measures of NPV and
overall reliability rating (see
Figure \@ref(fig:allocation-statistics-1)). The
overall reliability rating was created for the purpose of the experiment and
always varied alongside NPV. That is, overall reliability rating and NPV for the
target project were always both either higher or lower than the comparison
project. Participants entered their allocation data beneath this table in two
text boxes labelled *Project A allocation* and *Project B allocation*,
respectively.

[^integration]: A horizontally integrated company is one which is made up of
multiple businesses that operate in similar markets, and may have previously
been competitors [@gaughan2012]. A vertically integrated company, on the other
hand, is one which is made up of multiple business than operate in the same
market, but in different levels of the supply chain [@gaughan2012a].

[^structure]: A centralised organisational structure is one in which a company
decisions tend to come from a specific business unit or leader, whereas a
decentralised structure is one in which decisions can be made by separate units
or people independently [@kenton2021].

(ref:allocation-anecdote-only-1) Focal project display for the anecdote only condition in Experiment 1. Here, Project A was the target project and Project B was the comparison project.

```{r allocation-anecdote-only-1, fig.cap = "(ref:allocation-anecdote-only-1)"}
file.path(
  materials_1,
  "project_allocation_anecdote_only.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:allocation-statistics-1) Focal project display for the statistics only, anecdote & statistics, and anecdote & enhanced statistics conditions in Experiment 1. Here, Project A was the target project and Project B was the comparison project.

```{r allocation-statistics-1, out.width = "95%", fig.cap = "(ref:allocation-statistics-1)"}
file.path(
  materials_1,
  "project_allocation_statistics.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Anecdote

Participants who were presented with an anecdote (those in either the anecdote
only, anecdote & statistics, or anecdote & enhanced statistics conditions) were
shown a description of another business project and an accompanying analysis.
Figures \@ref(fig:anecdote-similarity-high-1)
and \@ref(fig:anecdote-similarity-low-1) show the anecdotes
for those in the high and low similarity conditions, respectively. The project
description had a similar layout to that of the focal projects. That is, it
contained information about the business name, location, integration, and
organisational structure of the business. It also detailed several predicted
features of the project. Beneath this description was a paragraph presenting an
analysis of why the project had failed. This paragraph referenced each of the
features in the description to justify the failure of the project.


Participants in the high similarity condition were shown a description of a
project from a business with the same type of investment as the target project
(Project A). All categorical attributes (e.g., location) were identical to those
in Project A, but all numerical attributes (e.g., oil extraction rate) were
lower. The analysis explained that the numerical attributes had failed because
they had not reached certain cut-offs. Critically, these cut-offs were all
higher than the matching values in Project A. This was done to ensure that the
numerical attributes in the anecdote appeared more relevant than those in
Project A. For instance, in Project A, oil extraction was set at 2,200 L/hr, and
in the anecdote it was 2,000 L/hr, while the cut-off was set at 3,000 L/hr.
Thus, the failure of the anecdotal project arising from insufficient oil
extraction would appear more relevant to the Project A because the oil
extraction in both the anecdotal project and Project A was lower than the
cut-off value. Note, however, that the participants did not receive an explicit
indication of whether these values were meant to generalise to other cases. This
means that any such inference would indicate that participants were sensitive to
the relational similarity between the two projects, and not just the surface
similarity of the project type.

(ref:anecdote-similarity-high-1) Anecdote for participants in the high similarity condition in Experiment 1.

```{r anecdote-similarity-high-1, fig.cap = "(ref:anecdote-similarity-high-1)"}
file.path(
  materials_1,
  "anecdote_similarity_high.png"
) %>%
  image_read() %>%
  image_trim()
```

(ref:anecdote-similarity-low-1) Anecdote for participants in the low similarity condition in Experiment 1.

```{r anecdote-similarity-low-1, fig.cap = "(ref:anecdote-similarity-low-1)"}
file.path(
  materials_1,
  "anecdote_similarity_low.png"
) %>%
  image_read() %>%
  image_trim()
```

#### Follow-up Questions

Participants who were shown the anecdote were subsequently presented with
follow-up questions. They were asked about how similar they believed the
anecdote was to the target project, how relevant it was to their allocations and
how relevant it would be for their judgements about other projects of that type
(see Appendix \@ref(follow-up-materials-1)).

### Procedure

Participants were introduced to the study through the general instructions
followed by the specific instructions for their condition. Participants were
then presented with the allocation task and a description of the focal projects.
All participants except those in the statistics only condition were also
presented with the anecdote description and analysis, and the follow-up
questions.
