## Results {#results-anecdotes-1}

### The Effect of Similarity on Anecdotal Bias

Anecdotal bias was tested by comparing the statistics only condition with both
the high- and low-similarity anecdote & statistics conditions (see
Figure \@ref(fig:plot-1-allocation-combined)). The omnibus one-way
ANOVA of these three conditions was significant,
`r results_1$allocation$condition`.
Evidence of anecdotal bias is seen when participants allocate more to the
statistics only condition than to the anecdote & statistics condition. Finding
this effect implies that the anecdote influenced participants to reduce their
allocation because the anecdote was unsuccessful. Planned comparisons show that
participants in the statistics only condition allocated more to the target
project compared with participants in the high-similarity anecdote & statistics
condition,
`r results_1$allocation$Combinedhigh_statisticsNA`; but not
the low-similarity anecdote with statistics condition,
`r results_1$allocation$Combinedlow_statisticsNA`. These findings
provide evidence of anecdotal bias in the high similarity condition only.

(ref:plot-1-allocation-combined) Mean allocation to the target project for the statistics only condition and the two anecdote & statistics conditions. Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-1-allocation-combined, fig.cap = "(ref:plot-1-allocation-combined)"}
plot_1$allocation_combined
```

### The Effect of Enhanced Statistics

In the enhanced statistics condition, we add an explanation of scientific
thinking to hint that aggregated data is likely to be more reliable than
anecdotes. The effect of enhanced statistics was investigated by testing the
interaction of anecdote similarity and evidence type (anecdote & statistics and
anecdote & enhanced statistics conditions, excluding the anecdote only and
statistics only conditions). As shown in
Figure \@ref(fig:plot-1-allocation), the two-way interaction was not
significant, `r results_1$allocation$Combined_enhanced_High_low`. Further, the
difference between the anecdote & statistics condition and the anecdote &
enhanced statistics condition (averaged over similarity conditions) was also not
significant, `r results_1$allocation$Combined_enhanced`. This suggests that
providing participants with information about how to think statistically is not
sufficient to facilitate a focus on statistics.

(ref:plot-1-allocation) Mean allocation to the target project, by anecdote similarity and evidence type conditions (excluding the statistics only condition). Error bars represent 95% confidence intervals. Raw data are plotted in the background.

```{r plot-1-allocation, fig.cap = "(ref:plot-1-allocation)"}
plot_1$allocation
```

### The Effect of Statistics

To identify the influence of statistics on participants' allocations we compared
the anecdotes only condition to the high similarity anecdote & statistics
condition (see Figure \@ref(fig:plot-1-allocation)). This tests
whether seeing the anecdote made participants disregard the statistics or
whether the statistics still influenced their decisions. We found that
participants allocated more in the high similarity anecdote & statistics
condition compared with the anecdote only condition,
`r results_1$allocation$High_Anecdote_combined`. This provides evidence of partial
anecdotal bias because the anecdote & statistics condition was both lower than
the statistics only condition (shown above) and higher than the anecdote only
condition.

### Relevance Ratings

Regression analyses were conducted to determine the relationship between
allocations and the follow-up relevance ratings. As shown in
Figure \@ref(fig:plot-1-lm-allocation-relevance-specific-alignment),
the specific relevance ratings interacted with similarity condition, 
`r results_1$lm$allocation_relevance_specific_alignment`. It appears that
specific relevance ratings were related to allocations, but only in the high
similarity condition. That is, those in the high similarity condition allocated
less to the target project the more relevant they considered the negative
anecdote. Furthermore, there were no significant associations with the general
relevance ratings. This suggests that participants applied reasoning to the
connection between the anecdote and the target project as opposed to simply
reacting to the failed project and associating that with that project's
industry.

(ref:plot-1-lm-allocation-relevance-specific-alignment) Mean allocation to the target project, by specific relevance rating and similarity condition. LOESS method was used for smoothing over trials and the shading represents 95% confidence intervals. Raw data are plotted in the background.

```{r plot-1-lm-allocation-relevance-specific-alignment, fig.cap = "(ref:plot-1-lm-allocation-relevance-specific-alignment)"} 
plot_1$lm$allocation_relevance_specific_alignment
```
